Impact of Education on Entrepreneurship - Data Gathering and Analysis

### 2014-11-27 GEMDataSource.Rmd
Added new GEM data

# Library required packages repmis, ridy, reshape2, plyr and WDI packages
library(plyr)
library(repmis)
library(tidyr)
library(reshape2)
library(WDI)

@@

1. $PercentIntention = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$

@@

3. $PercentOwner = PercentPerceived + PercentFear*PercentOpportunities + AnnualGDPGrowth$  
<br>

@@

# Import GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is

@@

@@

To review, the three regression equations used for this assignment are included below.

1. $PercentIntention = PercentPerceived(Perceived Capabilities) + GEM D01 way of teaching + PercentOpportunities(Perceived Opportunities)$

>>>>

# Library required packages repmis, ridy, reshape2, plyr and WDI packages
library(plyr)
library(repmis)
library(tidyr)
library(reshape2)
library(WDI)
library(foreign)

@@

1. $PercentIntention = PercentPerceived(Perceived Capabilities) + Way of Teaching + PercentOpportunities(Perceived Opportunities)$

@@

@@

# Import 2010GEM supportive teaching data as a proxy for how favourable to self-confidence a given education system is

@@

# Import GEM 2009 supportive teaching data
setwd('~/Assign2Education/GEMData')

GEM2006 <- read.spss('2006GEMNES.sav', to.data.frame = TRUE)
GEM2007 <- read.spss('2007GEMNES.sav', to.data.frame = TRUE)
GEM2008 <- read.spss('2008GEMNES.sav', to.data.frame = TRUE)
GEM2009 <- read.spss('2009GEMNESMDS.sav', to.data.frame = TRUE)
GEM2010 <- read.spss('2010GEMNES.sav', to.data.frame = TRUE)

Clean06 <- GEM2006[,c("KI06CTRY", "KI06D01_mean")]
Clean07 <- GEM2007[,c("ki07ctry", "ki07d01_")]
Clean08 <- GEM2008[,c("NES08COUNTRY", "NES08_D01_MEAN")]
Clean09 <- GEM2009[,c("NES09COUNTRY", "NES09_D01_MEAN")]
Clean10 <- GEM2010[,c("NES10CRNAME", "NES10_D01_MEAN")]

names(Clean06) <- gsub("KI06D01_mean", "2006", names(Clean06))
names(Clean07) <- gsub("ki07d01_", "2007", names(Clean07))

@@
